Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-20 ms.tex
fixing up a couple of figure captions

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Red crosses 
mark the best-fit parameters based on our Markov chain sampling of the 
posterior. The posterior distributions are in general extremely well-behaved, 
showing no multimodality or other pathological qualities. Our MCMC parameter 
estimates coincide well with the peaks in the gridded posteriors. The 
colorscale is linear in $log(P)$, with black representing the maximum of 
$log(P)$ and white representing $max(log(P))-5$. Left: Low S/N pixel at 
high latitude in the Galactic north. Center: High S/N pixel in the Polaris 
region. Right: Low S/N pixel at high latitude in the Galactic south.}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\epsfig{file=calib_ebv.eps, width=3.3in}
\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as function of
$\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$ and 
$|\beta|$$>$20$^{\circ}$.}
\end{center}
\end{figure}

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Light green
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posterior. The posterior distributions are in
general extremely well-behaved, showing no multimodality or other pathological 
qualities. Our MCMC parameter and uncertainty estimates are in good agreement 
with the gridded posteriors. The colorscale is linear in $log(P)$, with black 
representing the maximum of $log(P)$ and white representing $max(log(P))-5$. 
Left: Low S/N pixel at high latitude in the Galactic north. Center: High S/N 
pixel in the Polaris region. Right: Low S/N pixel at high latitude in the 
Galactic south.}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\epsfig{file=calib_ebv.eps, width=3.3in}
\caption{\label{fig:calib} Linear fit of $E(B-V)_{SSPP}$ as a function of
two-component $\tau_{545}$, restricting to $|b|$$>$20$^{\circ}$.}
\end{center}
\end{figure}
